Near Optimal Behavior with Approximate Abstraction

### 2016-02-04 paper/example_domains.tex
small modification to theory results, trimmed example domains a bit

% Description of visuals.
We provide graphical visuals of both ground $\acp{MDP}$ and resulting abstract $\acp{MDP}$. In our visuals, a grey circle indicates a state, while the colored arrows indicate transitions. The thickness of the arrow indicates how much reward is associated with that transition. In the ground \acp{MDP}, states are labeled with a number. In some abstract \acp{MDP}, we indicate which ground states were collapsed to each abstract state by labelling the abstract states with their constituent ground states (some are visually unwieldy and so were not labelled).

%Description of code base
Additionally, in hopes of promoting further investigation into approximate abstraction, we provide our code base (link redacted for review) which provides implementations for abstracting arbitrary \acp{MDP} and visualizing and evaluating the resulting abstract \acp{MDP}. We use the graph visualization library GraphStream~\cite{graphstream} and planning and \ac{RL} library, BURLAP~\cite{BURLAPCITATION}.

@@

NChain, pictured in Figure~\ref{fig:nchain-visual}, is a simple MDP heavily investigated in the Bayesian Reinforcement Learning literature due to the interesting exploration problem it poses~\cite{dearden1998bayesian}. In all states, the agent has two actions available: advance down the chain, or return to state 0. The agent receives a small positive reward, $r_{small}$ for returning to state 0, and no reward for advancing down the chain, unless the agent transitions to the last state in the chain. This transition provides a large positive reward, $r_{large}$. Transitions also have small slip probability, $\rho$, such that the applied action results in the wrong action.g In our implementation, we set $N=10$, $\rho=0.2$, $r_{small} = 0.2$, and $r_{large} = 1.0$.

% NChain Compression Visuals.
\begin{figure}[h]
\subfigure[Ground NChain]{
\includegraphics[width=0.48\columnwidth]{figures/ground_nchain.png}}
\subfigure[Abstract NChain]{
\includegraphics[width=0.48\columnwidth]{figures/abs_nchain.png}}
\label{fig:nchain-visual}
\caption{Comparison of Original NChain MDP and Abstract NChain MDP, under an $\epQ$ abstraction, with $\epsilon=0.5$}
\end{figure}

@@

Taxi has long been studied by the hierarchical reinforcement learning literature due to its natural decomposition into hierarchical subgoals~\cite{dietterich2000hierarchical}. The agent, operating in a grid world style domain, may move left, right, up, and down, as well as pickup a passenger and drop off a passenger. The goal is achieved when the agent has taken each passenger to its destination.

@@

Minefield is a particular variant of Grid World \cite{russell1995modern} with slip probability of $.2$.  The reward function is such that moving up in the top row of the grid receive $1.0$ reward, all other transitions receive $0.2$ reward, except for transitions to a random set of $\kappa$ states (which may include the top row) that receive $0$ reward (these are the states with mines in them, thus the name). During experimentation, we set $N=10, M=4, \epsilon=1.1, \kappa = 5, x = 0.01$. We visualize the original Minefield and the abstract Minefield in ~\ref{ref:minefield-visual}.

% Minefield Compression Visuals
\begin{figure}
\subfigure[Ground Minefield]{
\includegraphics[width=0.48\columnwidth]{figures/ground_minefield.png}}
\subfigure[Abstract Minefield]{
\includegraphics[width=0.48\columnwidth]{figures/abs_minefield.png}}
\label{fig:minefield-visual}
\caption{Comparison of Original Minefield MDP and Abstract MDP, under an $\epQ$ abstraction, with $\epsilon=1.1$}
\end{figure}

@@

The Random MDP domain we consider is as follows. There are $N$ states, and $K$ actions. For each state, each action can transition to two randomly selected (but fixed) states, each with probability $0.5$.

>>>>

% Description of visuals.
We provide graphical visuals of both ground \acp{MDP} and resulting abstract \acp{MDP}. In our visuals, a grey circle indicates a state, while the colored arrows indicate transitions. The thickness of the arrow indicates how much reward is associated with that transition. In the ground \acp{MDP}, states are labeled with a number. In the abstract \acp{MDP} we indicate which ground states were collapsed to each abstract state by labelling the abstract states with their ground states. %(some are visually unwieldy and so were not labelled).

%Description of code base
Additionally, in hopes of promoting further investigation into approximate abstraction, we provide our code base (link redacted for review) which provides implementations for abstracting arbitrary \acp{MDP} as well as visualizing and evaluating the resulting abstract \acp{MDP}. We use the graph visualization library GraphStream~\cite{graphstream} and planning and \ac{RL} library, BURLAP~\cite{BURLAPCITATION}.

@@

NChain, pictured in Figure~\ref{fig:nchain-visual}, is a simple MDP heavily investigated in the Bayesian Reinforcement Learning literature due to the interesting exploration problem it poses~\cite{dearden1998bayesian}. In all states, the agent has two actions available: advance down the chain, or return to state 0. The agent receives a small positive reward, $r_{small}$ for returning to state 0, and no reward for advancing down the chain, unless the agent transitions to the last state in the chain which provides a large positive reward, $r_{large}$. Transitions also have small slip probability, $\rho$, such that the applied action results in the wrong action. In our implementation, we set $N=10$, $\rho=0.2$, $r_{small} = 0.2$, and $r_{large} = 1.0$.

% NChain Compression Visuals.
\begin{figure}[h]
\subfigure[Ground NChain]{
\includegraphics[width=0.48\columnwidth]{figures/ground_nchain.png}}
\subfigure[Abstract NChain]{
\includegraphics[width=0.48\columnwidth]{figures/abs_nchain.png}}
\label{fig:nchain-visual}
\caption{Comparison of ground NChain \ac{MDP} and abstract NChain \ac{MDP}, under an $\epQ$ abstraction, with $\epsilon=0.5$}
\end{figure}

@@

Taxi has long been studied by the hierarchical reinforcement learning literature~\cite{dietterich2000hierarchical}. The agent, operating in a grid world style domain may move left, right, up, and down, as well as pickup a passenger and drop off a passenger. The goal is achieved when the agent has taken all passenger to their destinations.

@@

Minefield is a particular variant of Grid World \cite{russell1995modern} with slip probability of $x$. The reward function is such that moving up in the top row of the grid receive $1.0$ reward, all other transitions receive $0.2$ reward, except for transitions to a random set of $\kappa$ states (which may include the top row) that receive $0$ reward (these are the states with mines in them, thus the name). During experimentation, we set $N=10, M=4, \epsilon=1.1, \kappa = 5, x = 0.01$. We visualize the original Minefield and the abstract Minefield in Figure~\ref{fig:minefield-visual}.

% Minefield Compression Visuals
\begin{figure}
\subfigure[Ground Minefield]{
\includegraphics[width=0.48\columnwidth]{figures/ground_minefield.png}}
\subfigure[Abstract Minefield]{
\includegraphics[width=0.48\columnwidth]{figures/abs_minefield.png}}
\label{fig:minefield-visual}
\caption{Comparison of ground Minefield \ac{MDP} and abstract \ac{MDP}, under a $\epQ$ abstraction, with $\epsilon=1.1$}
\end{figure}

@@

The Random \ac{MDP} domain we consider is as follows. There are $N$ states, and $K$ actions. For each state, each action can transition to two randomly selected (but fixed) states, each with probability $0.5$.
